Methods

### 2023-12-20 clustering_analysis.qmd
Transformed data to % ethnicity and re-examined options for cluster number
Matching practices

```{r}
#| echo: false
# Read in the analysis RData file ----
library(factoextra)
library(cluster)
library(dplyr)
library(targets)
load("cluster_analysis_v1.Rdata")
```

@@

@@

@@

@@

@@

Should I break the practices up some how by taking out white?

>>>>

```{r}
#| echo: false
# Read in the analysis RData file ----
library(factoextra)
library(cluster)
library(dplyr)
library(targets)
library(GGally)
library(gt)
library(tidyverse)

load("cluster_analysis_v1.Rdata")
```

@@

::: panel-tabset
## Actual Numbers

## Percent

```{r}
#| echo: false
full_cats_percents_plot
```
:::

@@

::: panel-tabset
## Actual numbers

## Percent

```{r}
#| echo: false
five_cats_percents_plot
```
:::

@@

## Correlation Matrix

```{r}
#Correlation Matrix
ggcorr(full_cats,
       method = "pairwise",
       nbreaks = 10,
       hjust = 0.9,
       label = TRUE,
       label_size = 3,
       layout.exp = 3)+
  theme(legend.position = c(0.25,0.65))
```

## Scree Plots

::: panel-tabset
## All categories

```{r}
pca <- princomp(scale_full_cats)

screeplot(pca, npcs=14)
```

## Excluding White British

```{r}
pca2 <- princomp(scale_full_cats_percents_ex_whitebritish)

screeplot(pca2, npcs=14)
```
:::

@@

### Alternative K-Medoid models

#### Experiment with removal of White British completely but leave all practices in the dataset

```{r}
pams_full_cats_percents_ex_whitebritish8_clusters_plot
```

```{r}
final_data_full_cats_percents_ex_whitebritish8_clusters |>
  rownames_to_column(var = 'practice_code') |>
  group_by(cluster)|>
  count("practice_code")|>
  select(cluster,n) |>
  gt()
```

![](secret/Picture4.png){fig-align="center"}

#### Experiment with removal of practice with \> 85% White British manually into their own group

```{r}
pams_full_cats_percents_ex_85whitebritish7_clusters_plot
```

![](secret/Picture5.png){fig-align="center"}

@@

### 2023-12-20 methods.qmd
Test clustering methods
Matching practices

>>>>

<https://www.statology.org/k-medoids-in-r/>

https://www.rdocumentation.org/packages/cluster/versions/2.1.6

look at 18:50 in this video: https://www.youtube.com/watch?v=dKXTNxNDpMA

## Mapping new GP practices to old

### To obtain CHD prevalence for as many new practices as possible

```{r}
library(stringr)
gp_lsoa_with_eth_sum <- tar_read(gp_lsoa_with_eth_sum) |> as_tibble()

metric1 <- tar_read(metric1) |> as_tibble()

gp_history <- tar_read(gp_history) |> as_tibble()

match_gps <- gp_lsoa_with_eth_sum |> left_join(metric1, join_by(practice_code==AreaCode)) |>
  mutate(chdprev=case_when(Value>0 ~ Value))

#select just gps with missing data
missing_data_gps <- match_gps |> 
  filter(Value<0|is.na(Value)==TRUE) |>
  select(practice_code)

#get the postcodes
missing_data_gps <- missing_data_gps |> 
  left_join(gp_history, join_by(practice_code==org_code))|>
  select(practice_code,postcode)|>
  mutate(part_practice_code=substr(postcode,1,str_length(postcode)-1))

#remove active practices from the gp_history and attach the CHD prevalence(metric1)
gp_history <- gp_history |> 
  mutate(part_practice_code=substr(postcode,1,str_length(postcode)-1)) |>
  filter(status_code!="A") |>
  inner_join(metric1, join_by(org_code==AreaCode))

test <- missing_data_gps |> left_join(gp_history, join_by(part_practice_code==part_practice_code))

```
